 \documentclass[a4paper,BCOR=15mm,bibtotoc,headings=optiontohead, cleardoubleplain]{scrbook}

\usepackage{fontspec}
\defaultfontfeatures{Ligatures=TeX}
  \setmainfont{Tex Gyre Pagella}
  \setsansfont{Tex Gyre Heros}
  \setmonofont{Latin Modern Mono}

\newfontfamily{\titleparticles}[Scale=MatchUppercase]{Fira Sans}

\setkomafont{caption}{\small}

\usepackage{scrpage2}
  \pagestyle{scrheadings}
  \renewcommand*{\figureformat}{Fig.~\thefigure\autodot}
  \renewcommand*{\tableformat}{Tab.~\thetable\autodot}


\usepackage{csquotes}
\usepackage{polyglossia}
\setdefaultlanguage{english}

\usepackage[style=numeric-comp,sorting=none,backend=biber,firstinits=true]{biblatex}
\DeclareFieldFormat[article]{title}{\enquote{#1},}
\DeclareFieldFormat[report]{title}{\enquote{#1},}
\DeclareFieldFormat[book]{title}{\enquote{#1},}
\renewcommand*{\newunitpunct}{\addcomma\space}%Komma statt Punkt als trennzeichen zwischen autoren/titel
\DefineBibliographyStrings{english}{andothers = {{et\:al\adddot}},}%et al statt u.a.
\addbibresource{bibliography.bib}

\usepackage{hyperref}
\hypersetup{
    pdfauthor = {Alex Birnkraut, alex.birnkraut@tu-dortmund.de},
    pdftitle = {Measurement of CPV in Bd->Dpi},
    pdfsubject = {Time dependent CP violation measurement},
    pdfkeywords = {HEP, CERN, LHC, LHCb, CP violation, b physics, flavour physics},
    pdfcreator = {LaTeX with hyperref package},
    pdfproducer = {lualatex}
    }
\usepackage{slashed}

\usepackage{microtype}

\usepackage{mathtools}
\usepackage[locale=DE,input-ignore={.},input-decimal-markers={,}]{siunitx}
\usepackage{xfrac}
\usepackage{unicode-math}
\usepackage{bm}
\setmathfont{Tex Gyre Pagella Math}

\usepackage{cleveref}
\crefname{chapter}{Ch.\@}{Chs.\@}
\crefname{section}{Sec.\@}{Secs.\@}
\crefname{subsection}{Sec.\@}{Secs.\@}
\crefname{figure}{Fig.\@}{Figs.\@}
\crefname{table}{Tab.\@}{Tab.\@}
\crefname{equation}{Eq.\@}{Eqs.\@}

\usepackage{enumerate}

\usepackage[ugly]{nicefrac}

\usepackage{graphicx}

\usepackage{booktabs}
\usepackage{tabulary}
\usepackage{threeparttable}

% only for debugging and review
\usepackage{blindtext}
\usepackage{lineno}

\usepackage{ifthen}
\newboolean{uprightparticles}
\setboolean{uprightparticles}{false} %Set true for upright particle symbols
\usepackage{xspace}
\usepackage{upgreek}
\input{lhcb-symbols-def}

%%% Workaround to get math bold & without serifs in title's and headings
\DeclareMathAlphabet{\mathtestfit}{\encodingdefault}{\sfdefault}{m}{sl}
\SetMathAlphabet{\mathtestfit}{bold}{\encodingdefault}{\sfdefault}{bx}{sl}
\newcommand{\boldssmath}[1]{\bm{\mathtestfit{#1}}}
\newcommand{\ssmath}[1]{\mathtestfit{#1}}

\begin{document}

\frontmatter
  \input{titlepage}
  \input{abstract}
  \tableofcontents

\mainmatter
  \include{01introduction/introduction}
  \include{02theory/theory}
  \include{03CPV/cpv}
  \include{04lhcb/lhcb}
  \include{05selection/selection}
  \include{06MassFit/massfit}
  \include{07FlavourTagging/tagging}
  \include{08TimeFit/timefit}
  \include{09Systematics/systematics}
  \include{10Result/result}
  \include{11Conclusion/conclusion}

\backmatter
  \printbibliography

\newpage
\pagestyle{empty}
\input{acknowledgements}
\newpage
% \input{versicherung}
\end{document}

